Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-06-09 reports/manuscript/supplemental_changes.tex
Move figure captions to the end.
Put figures back in their place.

\section{\added{Data harmonization in the HBN dataset}}

\added{\Cref{fig:hbn-site-bp:fa,fig:hbn-site-bp:md} show the bundle profiles for the HBN dataset separated by scanner site: Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC). We see strong site differences in both FA and MD profiles. Conversely, \cref{fig:hbn-site-age-dist} shows that the age distributions at each site are similar. ComBat effectively harmonizes the scanner site differences, as shown in \cref{fig:hbn-harmonized-bp:fa,fig:hbn-harmonized-bp:md}.}

>>>>

\section{Data harmonization in the HBN dataset}

\Cref{fig:hbn-site-bp:fa,fig:hbn-site-bp:md} show the bundle profiles for the HBN dataset separated by scanner site: Rutgers Rutgers University Brain Imaging Center (RU) and the CitiGroup Cornell Brain Imaging Center (CBIC). We see strong site differences in both FA and MD profiles. Conversely, \cref{fig:hbn-site-age-dist} shows that the age distributions at each site are similar. ComBat effectively harmonizes the scanner site differences, as shown in \cref{fig:hbn-harmonized-bp:fa,fig:hbn-harmonized-bp:md}.
